Making Sequential Programs Deterministic

### 2019-04-06 randoop-case-study.tex
Explain fifth Randoop bug

>>>>

\item[Moderate issues]
  \strut
\begin{description}
\item[\bugHashMapOutput]
While printing diagnostic output, Randoop iterated over a \<HashMap> in
arbitrary order, making the output difficult to compare across different
executions, or even to find information in.
The class already implemented \<Comparable>, so
the developers changed \<methodWeights.keySet()> to
\codeid{new TreeSet<>(methodWeights.keySet()} in a \<for> loop (commit
\todo{TO DO}).
% This was actually introduced after the coding sprint.  Maybe some other
% defects were too, so our criticism should be about regressions rather
% than not finding them in the first place.
\end{description}
